Turbulence and Particle Acceleration in Giant Radio Haloes: the Origin of Seed Electrons

### 2016-06-23 paper.tex
further questions and additions

An obvious candidate for $\tau_{\rm decay}$ is: 
\begin{equation}
\tau_{\rm edd} = \frac{L}{\varv_{\rm c}}
\end{equation}
i.e., the eddy turnover time at the outer scale. This is subject to
uncertainties about the location of the outer scale $L$; estimates in the
literature range from $L \sim 0.1-1$ Mpc. It is also worth remembering that MHD
turbulence only applies for $l < l_{\rm A}$, where $l_{\rm A}$ is the Alfv{\'e}n
scale where $\varv \sim \varv_{\rm A}$. Invoking fast modes, Kraichnan scalings,
etc., is only valid below these scales. For $l > l_{\rm A}$, turbulence is
basically hydrodynamic and follows the universal Kolmogorov scaling. The
momentum diffusion coefficient can thus be split up into two components:
\begin{equation}
D_{pp} = D_{pp}^{\rm HD}[l_{\rm A} < l < L] + D_{pp}^{\rm MHD}[l_{\rm cut} < l < l_{\rm A}]
\end{equation}
From equations (\ref{eqn:diffusion}) and (\ref{eqn:k_W}), and assuming Kolmogorov turbulence from $l_{\rm A} < l < L$ and Kraichnan turbulence from $l_{\rm cut} < l < l_{\rm A}$, we get: 
\begin{equation}
  \frac{D_{pp}^{\rm HD}}{D_{pp}^{\rm MHD}}
  = \frac{\cp{2}k_L^{2/3}k_{\rm A}^{1/3} \varv_{\rm c}^{2}}{k_{\rm A}^{1/2}k_{\rm cut}^{1/2} \varv_{\rm A}^{2}}
  = \cp{2 \left(A \mathcal{M}_\rmn{A}\right)^{-1/2}} \beta = 0.5 \left( \frac{\beta}{50} \right) 
\end{equation}
where we have used $k_{\rm A} = k_L \mathcal{M}_{\rm A}^{3}$ (from Kolmogorov scalings), and $\mathcal{M}_{\rm A} = \varv_{\rm c}/\varv_{\rm A}$ is the Alfv{\'e}n Mach number of the turbulence, $\beta \approx c_{\rm s}^{2}/\varv_{\rm A}^{2}$, and the cutoff scale $k_{\rm cut}$ (equation \ref{eqn:k_c}).  Thus, the contribution of the two regimes are comparable (as we shall see later, this is not true if one incorrectly assumes Kraichnan scalings apply from the outer scale $L$; this boosts the contribution of the scales where $l_{\rm A} < l < L$ by a factor $\mathcal{M}_{\rm A}^{1/2}$). 
Henceforth, we can consider the outer scale of the fast modes to be $l_{\rm A}$, with velocity $\varv_{\rm A}$. The turbulent reacceleration time is: 
\begin{equation}
\tau_{\rm D} = \frac{p^{2}}{4 D_{pp}} = C_{\rm D} A^{1/2} c k_{\rm A} \frac{\varv_{\rm A}^{2}}{c_{\rm S}^{2}}
\label{eqn:tau_D} 
\end{equation}
\cp{[The previous equation is wrong (you can see this by checking the units). Instead I get:]
\begin{equation}
\tau_{\rm D} = \frac{p^{2}}{4 D_{pp}} = C_{\rm D} \left(A\mathcal{M}_\rmn{A}\right)^{-1/2} \frac{c}{k_{\rm A}} \frac{c_{\rm s}^{2}}{\varv_{\rm A}^{4}}
\label{eqn:tau_D} 
\end{equation}
}
where $C_{\rm D} = 2/(5 \upi)$, $A\approx 11000$, and we have used equation (\ref{eqn:k_c}). The turbulent decay time is given by the cascade time of fast modes (\citealt{2004ApJ...614..757Y}; see equation \ref{eqn:cascade}): 
\begin{equation}
\tau_{\rm decay} = \frac{c_{\rm s}}{\varv_{\rm A}^{2} k_{\rm A}^{}}\,.
\label{eqn:tau_decay} 
\end{equation}
\cp{[This agrees with Eqn. (3) of \citet{2004ApJ...614..757Y} but appears to disagree with our equation (\ref{eqn:tau_l}): Peng, do you understand this apparent contradiction? Can we motivate this important equation?]}
This can be related to the eddy turnover time at the outer scale $\tau_{\rm edd}$ from $l_{\rm A} = L \mathcal{M}_{\rm A}^{-3}$ to: 
\begin{equation}
\tau_{\rm decay} =\frac{L}{\varv_{\rm c}} \left(\frac{c_{\rm s}}{\varv_{\rm c}} \right)^{2} \frac{\varv_{\rm A}}{c_{\rm s}} = 0.7 \, \tau_{\rm edd} \left(\frac{\tilde{X}_{\rm tu}}{0.2}\right)^{-1}  \left(\frac{\beta}{100} \right)^{-1/2}
\end{equation}
\cp{[I get 0.08 as prefactor mainly because of the $2\upi$ conversion from $k$ to $L$.]}
where we have used $\tilde{X}_{\rm tu} \approx (\varv_{\rm c}/c_{\rm s})^{2}$ and $c_{\rm s}/\varv_{\rm A} = \beta^{1/2}$. Thus $\tau_{\rm decay} \sim \tau_{\rm edd}$, but we prefer to use the expression for $\tau_{\rm edd}$, since it is more physically correct and leads to more revealing scalings.

@@

It is also worth exploring the effect of Burgers' turbulence (weak shocks). From equations (\ref{eqn:diffusion}) and (\ref{eqn:k_W}), we find: 
\begin{equation}
\frac{D_{pp}^{\rm Burgers}}{D_{pp}^{\rm MHD}} = \left( \frac{\beta}{X_{\rm tu} A} \right)^{1/2} = 0.15 \left( \frac{\beta}{50} \right)^{1/2} \left( \frac{X_{\rm tu}}{0.2} \right)^{-1/2} 
\end{equation}
where we have set $\langle k \rangle_{\mathcal{W}} \approx k_L$ for Burgers' turbulence, i.e. all power is at large scales. This weighting towards larger scales implies a much lower wave-particle interaction rate and thus a diffusion coefficient which is smaller than standard TTD on thermal particles by an order of magnitude. Since $\langle k \rangle_{\mathcal{W}} \approx k_L$ is independent of the cutoff scale $k_{\rm cut}$, this conclusion is unchanged if plasma instabilities regulate the thermal particle mean free path and TTD operates on relativistic particles instead. Since standard TTD on thermal particles was already potentially problematic (equation \ref{eqn:ratios_TTD}), we conclude, in agreement with other assessments \citep{miniati15,brunetti16_review}, that if Burgers turbulence dominates, then turbulent reacceleration will be ineffective\footnote{Note also that since there is no real cascade in Burgers' turbulence, but direct transfer of power from large to small scales, the dissipation time is potentially short. In this case, $\tau_{\rm cl} \sim \tau_{\rm drive}$, the driving time, rather than the turbulent dissipation time.}.

>>>>

An obvious candidate for $\tau_{\rm decay}$ is: 
\begin{equation}
\tau_{\rm edd} = \frac{L}{\varv_{\rm c}}
\end{equation}
i.e., the eddy turnover time at the outer scale. This is subject to
uncertainties about the location of the outer scale $L$; estimates in the
literature range from $L \sim 0.1-1$ Mpc. It is also worth remembering that MHD
turbulence only applies for $l < l_{\rm A}$, where $l_{\rm A}$ is the Alfv{\'e}n
scale where $\varv \sim \varv_{\rm A}$. Invoking fast modes, Kraichnan scalings,
etc., is only valid below these scales. For $l > l_{\rm A}$, turbulence is
basically hydrodynamic and follows the universal Kolmogorov scaling. The
momentum diffusion coefficient can thus be split up into two components:
\begin{equation}
D_{pp} = D_{pp}^{\rm HD}[l_{\rm A} < l < L] + D_{pp}^{\rm MHD}[l_{\rm cut} < l < l_{\rm A}]
\end{equation}
From equations (\ref{eqn:diffusion}) and (\ref{eqn:k_W}), and assuming Kolmogorov turbulence from $l_{\rm A} < l < L$ and Kraichnan turbulence from $l_{\rm cut} < l < l_{\rm A}$, we get: 
\begin{equation}
  \frac{D_{pp}^{\rm HD}}{D_{pp}^{\rm MHD}}
  = \frac{\cp{2}k_L^{2/3}k_{\rm A}^{1/3} \varv_{\rm c}^{2}}{k_{\rm A}^{1/2}k_{\rm cut}^{1/2} \varv_{\rm A}^{2}}
  = \cp{2 \left(A \mathcal{M}_\rmn{A}\right)^{-1/2}} \beta = 0.5 \left( \frac{\beta}{50} \right) 
\end{equation}
\cp{[This assumes the energy equipartition argument (by Sarkar) for $D_{pp}^\rmn{MHD}$ and for $D_{pp}^\rmn{HD}$; is this justified at the sme time? if so, why? and we should explain this in a footnote.]}
where we have used $k_{\rm A} = k_L \mathcal{M}_{\rm A}^{3}$ (from Kolmogorov scalings), and $\mathcal{M}_{\rm A} = \varv_{\rm c}/\varv_{\rm A}$ is the Alfv{\'e}n Mach number of the turbulence, $\beta \approx c_{\rm s}^{2}/\varv_{\rm A}^{2}$, and the cutoff scale $k_{\rm cut}$ (equation \ref{eqn:k_c}).  Thus, the contribution of the two regimes are comparable (as we shall see later, this is not true if one incorrectly assumes Kraichnan scalings apply from the outer scale $L$; this boosts the contribution of the scales where $l_{\rm A} < l < L$ by a factor $\mathcal{M}_{\rm A}^{1/2}$). 
Henceforth, we can consider the outer scale of the fast modes to be $l_{\rm A}$, with velocity $\varv_{\rm A}$. The turbulent reacceleration time is: 
\begin{equation}
\tau_{\rm D} = \frac{p^{2}}{4 D_{pp}} = C_{\rm D} A^{1/2} c k_{\rm A} \frac{\varv_{\rm A}^{2}}{c_{\rm S}^{2}}
\label{eqn:tau_D} 
\end{equation}
\cp{[The previous equation is wrong (you can see this by checking the units). Instead I get:]
\begin{equation}
\tau_{\rm D} = \frac{p^{2}}{4 D_{pp}} = C_{\rm D} \left(A\mathcal{M}_\rmn{A}\right)^{-1/2} \frac{c}{k_{\rm A}} \frac{c_{\rm s}^{2}}{\varv_{\rm A}^{4}}
\label{eqn:tau_D} 
\end{equation}
}
where $C_{\rm D} = 2/(5 \upi)$, $A\approx 11000$, and we have used equation (\ref{eqn:k_c}). The turbulent decay time is given by the cascade time of fast modes (\citealt{2004ApJ...614..757Y}; see equation \ref{eqn:cascade}): 
\begin{equation}
\tau_{\rm decay} = \frac{c_{\rm s}}{\varv_{\rm A}^{2} k_{\rm A}^{}}\,.
\label{eqn:tau_decay} 
\end{equation}
\cp{[This agrees with Eqn. (3) of \citet{2004ApJ...614..757Y} but appears to disagree with our equation (\ref{eqn:tau_l}): Peng, do you understand this apparent contradiction? Can we motivate this important equation?]}
This can be related to the eddy turnover time at the outer scale $\tau_{\rm edd}$ from $l_{\rm A} = L \mathcal{M}_{\rm A}^{-3}$ to: 
\begin{equation}
\tau_{\rm decay} =\frac{L}{\varv_{\rm c}} \left(\frac{c_{\rm s}}{\varv_{\rm c}} \right)^{2} \frac{\varv_{\rm A}}{c_{\rm s}} = 0.7 \, \tau_{\rm edd} \left(\frac{\tilde{X}_{\rm tu}}{0.2}\right)^{-1}  \left(\frac{\beta}{100} \right)^{-1/2}
\end{equation}
\cp{[I get 0.08 as prefactor mainly because of the $2\upi$ conversion from $k$ to $L$.]}
where we have used $\tilde{X}_{\rm tu} \approx (\varv_{\rm c}/c_{\rm s})^{2}$ and $c_{\rm s}/\varv_{\rm A} = \beta^{1/2}$. Thus $\tau_{\rm decay} \sim \tau_{\rm edd}$, but we prefer to use the expression for $\tau_{\rm edd}$, since it is more physically correct and leads to more revealing scalings.

@@

It is also worth exploring the effect of Burgers' turbulence (weak shocks). \cp{Burgers' turbulence is distinct from other forms of turbulence in that it violates locality in $k$-space--i.e., power does not gradually cascade, but instead can directly jump from large to small scales via a network of weak shocks. Since the Fourier transform of a step function goes as $k^{-1}$, Burgers turbulence has a power spectrum of $P(k) \propto k^{-2}$.} From equations (\ref{eqn:diffusion}) and (\ref{eqn:k_W}), we find: 
\begin{equation}
\frac{D_{pp}^{\rm Burgers}}{D_{pp}^{\rm MHD}} = \left( \frac{\beta}{X_{\rm tu} A} \right)^{1/2} = 0.15 \left( \frac{\beta}{50} \right)^{1/2} \left( \frac{X_{\rm tu}}{0.2} \right)^{-1/2} 
\end{equation}
where we have set $\langle k \rangle_{\mathcal{W}} \approx k_L$ for Burgers' turbulence, i.e. all power is at large scales. This weighting towards larger scales implies a much lower wave-particle interaction rate and thus a diffusion coefficient which is smaller than standard TTD on thermal particles by an order of magnitude. Since $\langle k \rangle_{\mathcal{W}} \approx k_L$ is independent of the cutoff scale $k_{\rm cut}$, this conclusion is unchanged if plasma instabilities regulate the thermal particle mean free path and TTD operates on relativistic particles instead. Since standard TTD on thermal particles was already potentially problematic (equation \ref{eqn:ratios_TTD}), we conclude, in agreement with other assessments \citep{miniati15,brunetti16_review}, that if Burgers turbulence dominates, then turbulent reacceleration will be ineffective\footnote{Note also that since there is no real cascade in Burgers' turbulence, but direct transfer of power from large to small scales, the dissipation time is potentially short. In this case, $\tau_{\rm cl} \sim \tau_{\rm drive}$, the driving time, rather than the turbulent dissipation time.}.
